Data Specialization for a Staged Lambda Calculus

### 2015-02-28 paper/examples.tex
minor syntax bug

1`//dot : vec * vec -> $int
fun dot (
  (3`gr{`1`xliteralone`3`}`1`,`3`gr{`1`yliteralone`3`}`1`,next{`2`zliteralone`1`}): vec,
  (3`gr{`1`xliteraltwo`3`}`1`,`3`gr{`1`yliteraltwo`3`}`1`,next{`2`zliteraltwo`1`}): vec) = 
next{
  2`prev{`1`hold `3`gr{`1`(x1*x2) + (y1*y2)`3`}`2`} + (z1*z2)`
1`}`
\end{lstlisting}
%
The body of \texttt{dot} is a \rmint{} term at world \bbtwo\ containing a
\rmint\ computation of \texttt{(x1*x2) + (y1*y2)} which is promoted from world
\bbonep\ to world \bbtwo. We would expect the first stage of the split program
to take the first two coordinates of each vector and perform that first-stage
computation; and the second stage to take the final coordinates and the result
of the first stage, then multiply and add.

@@

fun qs1 (l : list, k : unit) = 
  ((), case l of
    Empty => Leaf
  | Cons (h,t) => 
      Branch (
        let (left,right,n) = partition (h,t) in
        (n, #2 (qs1 left k), h, #2 (qs1 right k))))`

>>>>

1`dot : vec * vec -> $int
fun dot (
  (3`gr{`1`xliteralone`3`}`1`,`3`gr{`1`yliteralone`3`}`1`,next{`2`zliteralone`1`}): vec,
  (3`gr{`1`xliteraltwo`3`}`1`,`3`gr{`1`yliteraltwo`3`}`1`,next{`2`zliteraltwo`1`}): vec) = 
next{
  2`prev{`1`hold `3`gr{`1`(x1*x2) + (y1*y2)`3`}`2`} + (z1*z2)`
1`}`
\end{lstlisting}
%
The body of \texttt{dot} is a \rmint{} term at world \bbtwo\ containing a
\rmint\ computation of \texttt{(x1*x2) + (y1*y2)} which is promoted from world
\bbonep\ to world \bbtwo. We would expect the first stage of the split program
to take the first two coordinates of each vector and perform that first-stage
computation; and the second stage to take the final coordinates and the result
of the first stage, then multiply and add.

@@

fun qs1 (l : list, k : unit) = 
  ((), case l of
    Empty => Leaf
  | Cons (h,t) => 
      Branch (
        let val (left,right,n) = partition (h,t) in
        (n, #2 (qs1 left k), h, #2 (qs1 right k))))`
